Challenges to the Two-Infall Scenario by Large Stellar Age Catalogs

### 2025-07-03 src/tex/ms.tex
Updates from Overleaf

% The parameters of Equation \ref{eq:infall-rate} have important effects on the chemical evolution of the model. 
% Previous studies of the two-infall model have adopted values for the infall parameters of $\tau_1\sim0.1-1\,{\rm Gyr}$, $\tau_2\sim3-10\,{\rm Gyr}$, and $t_{\rm max}\sim3-5\,{\rm Gyr}$. 
Previous studies have adopted a wide range of parameters for Equation \ref{eq:twoinfall-ifr}. Figure \ref{fig:twoinfall-parameters} illustrates the effect of varying the infall parameters on gas abundance tracks and stellar abundance distributions in a one-zone model with \yZ{1}. The first infall timescale $\tau_1$, shown in panel (a), primarily affects the stellar distribution along the high-$\alpha$ sequence. Though $\tau_1$ has an apparently large effect on the size of the low-$\alpha$ loop, the effect on the stellar abundance distribution of the low-$\alpha$ sequence is quite small due to the low number of stars formed between $t\sim3-6\,{\rm Gyr}$. We adopt $\tau_1=1\,{\rm Gyr}$ for our fiducial value, in line with \citet{spitoni_galactic_2020} but longer than, e.g., \citet{nissen_high-precision_2020} or \citet{spitoni_apogee_2021}, in order to set the peak of the high-$\alpha$ sequence at $\mathOFe\approx+0.3$.

@@

\begin{figure}
    \centering
    \includegraphics[width=\onecolumn]{figures/gas_abundance_evolution.pdf}
    \caption{The abundance evolution of three one-zone models with different yield sets and outflow mass-loading factors. Table \ref{tab:yields} presents the population-averaged yields for each model. The gray points plot the abundances of APOGEE stars with NN ages from \citet{leung_variational_2023} from the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $0\leq|z|<0.5\kpc$). The black points with error bars indicate the mode of the abundance data in 1 Gyr-wide age bins, and the gray error bars along the bottom of each panel indicate the median age and abundance errors as a function of age.}
    \label{fig:yield-outflow}
\end{figure}

@@

\subsection{The Local Abundance Topology}
\label{sec:abundance-distributions}

@@

\subsection{Global Abundance Distributions}
\label{sec:disk-abundances}

\subsubsection{The [O/Fe] Distribution}

@@

\subsubsection{The Best Model}
\label{sec:ofe-feh-best}

>>>>

% The parameters of Equation \ref{eq:infall-rate} have important effects on the chemical evolution of the model. 
% Previous studies of the two-infall model have adopted values for the infall parameters of $\tau_1\sim0.1-1\,{\rm Gyr}$, $\tau_2\sim3-10\,{\rm Gyr}$, and $t_{\rm max}\sim3-5\,{\rm Gyr}$. 
Previous studies have adopted a wide range of parameters for Equation \ref{eq:twoinfall-ifr}. Figure \ref{fig:twoinfall-parameters} illustrates the effect of varying the infall parameters on gas abundance tracks and stellar abundance distributions in a one-zone model with \yZ{1}. The first infall timescale $\tau_1$, shown in panel (a), primarily affects the stellar distribution along the high-$\alpha$ sequence. Though $\tau_1$ has an apparently large effect on the size of the low-$\alpha$ loop, the effect on the stellar abundance distribution of the low-$\alpha$ sequence is small due to the low number of stars formed between $t\sim3-6\,{\rm Gyr}$. We adopt $\tau_1=1\,{\rm Gyr}$ for our fiducial value, in line with \citet{spitoni_galactic_2020} but longer than, e.g., \citet{nissen_high-precision_2020} or \citet{spitoni_apogee_2021}, in order to set the peak of the high-$\alpha$ sequence at $\mathOFe\approx+0.3$.

@@

\begin{figure}
    \centering
    \includegraphics[width=\onecolumn]{figures/gas_abundance_evolution.pdf}
    \caption{The ISM abundance evolution at $R_{\rm gal}=8\kpc$ of three multi-zone models at different yield scales (see Table \ref{tab:yields}). The gray points plot the abundances of APOGEE stars with NN ages from \citet{leung_variational_2023} from the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $0\leq|z|<0.5\kpc$). The black points indicate the mode of the abundance data in 1 Gyr-wide age bins, and the gray error bars along the bottom of each panel indicate the median age and abundance errors as a function of age. The left-hand marginal panels show the predicted (blue, pink, and green) and observed (gray) stellar abundance distributions, which are boxcar-smoothed with a width of 0.05 dex for visual clarity.
    {\bf Key takeaway:} All models feature a major dilution event 9 Gyr ago, and the \yZ{1} model re-enriches the most slowly.}
    \label{fig:yield-outflow}
\end{figure}

@@

\subsection{The [O/Fe] Distribution}
\label{sec:abundance-distributions}

@@

% \subsection{Global Abundance Distributions}
% \label{sec:disk-abundances}

% \subsubsection{The [O/Fe] Distribution}

@@

\subsection{The Best Model}
\label{sec:ofe-feh-best}
